### 2012-08-03 Doc/VRIPHYS2012/vriphys2012.tex
changes to fit into 10 page limit
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@452 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

%%% ADD COMMENTS=
\usepackage{color} 
\newcommand{\CD}[1]{{\color{magenta}{\textbf{C: #1}}}}

@@

\FigureWI{stages}
{Two stages of interpolation: First, from triangular with 6DOF nodes (a) a mesh of control points (b) is computed.
Then based on definition of the B\'ezier triangle a surface (c) is interpolated.}

@@

\Figure{0.8\linewidth}{bezier2}
{Cubic B\'ezier triangle with mesh of 10 control points.}

@@

The cubic B\'ezier triangles are defined by a mesh of 10 control points each, however the
simulated object is usually described by a triangular mesh possibly with normals.
A procedure for construction of initial B\'zier mesh is necessary.
We construct the initial B\'ezier mesh by taking into account the curvature of the triangular
mesh. Note that special care has to be taken to maintain
the continuity between elements across the nodes and edges, 
we partially employ the method described in \cite{Ubach2010} to maintain
$C^0$ continuity. Each of the control points on the edge is
computed as the intersection of (\CD{Need to do a figure of this}):

@@

\Figure{0.8\linewidth}{segments2}
{Internal nodes of control mesh are connected to the corner nodes by kinematic link (shown in blue).}

@@

(\CD{TODO add a figure to illustrate the explanation})

@@

Because the deflection field for the element is non-linear \eqref{eq-bez-delta}
in position the integrals \eqref{eq-Km} and \eqref{eq-Kb} have to be computed using
numerical integration. In our implementation we employ 6-point Gaussian
quadrature for integration over triangle area.
\CD{TODO: figure + gives the formula of the quadrature...}
% TODO: add ref
% TODO: add abscissas/weights?

@@

Which means we use the same expression to interpolate the velocity only by
substituting the velocities at control points. 
For the corner \CD{\sout{nodes} $\rightarrow$ control points}  we
already have the velocities $V_i$. For the internal \CD{\sout{nodes} $\rightarrow$ control points}  we need to compute
them. We again make use of the kinematic link between nodes and control points.
%solve the problem of computing the velocity of a point attached to the moving rigid body.
For the edge points we applied to motion of a rigid body:
%
\begin{eqnarray}
    V_j = V_i + \omega_i \times P_{i-j}
\end{eqnarray}
%
where $i$ is the index of the corner node the edge node is attached to and
$\omega_i$ is the angular velocity at the node. For the central node
the formula is based on the derivate of equation \eqref{eq-central2}:
%
\begin{eqnarray}
    V_{10} = \frac{1}{3} \sum_{i=1}^3 \left( V_i + \omega_i \times P_{i-10} \right)
\end{eqnarray}

@@

% TODO:
% \CD{ - On this section,  we can maybe add some results from the CBM paper you did with Stephan especially  the figure 9 that illustrates the 3d contribution we list in the intro: i.e. Mapping of high resolution mesh on the curved surface of the shell.}
% -- Not enough space?

@@

\FigureW{0.75\linewidth}{chd}
{Screenshots of the simulation system prototype for different surgical
procedures used to repair a coarctation of an aortic arch. The screenshots
are enriched with overlay delineations.}

Surgical interventions in infants with congenitally malformed great arteries
and hearts are extremely challenging due to the complex and heterogeneous
nature of their disease patterns. At present, cardiac surgeons rely on
non-invasive imaging for patient-specific examination and a set of preoperative
sketches with varying approaches to the surgical procedure. However, the most
promising approach is often chosen during the actual open-heart surgery, when
surgeons get a more concrete idea of possible outcomes. Finalizing this
decision during an on-pump cardiac surgery is further complicated by deflated
blood vessels since it is difficult to imagine their exact change of shape
caused by the intervention. The important decisions have to be made in very
short time and are strongly dependent on the surgeon's experience.

@@

%%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%
%% TODO: is this OK for anonymity?
%The presented element has been successfully implemented in SOFA framework
%\cite{Faure2012} for real-time surgical simulations. It has been evaluated
%on several applications.
%

@@

It fixes problems of the previous model \cite{Comas2010c} based on cubic polynomials, namely:

    \item Element is based on all 6 DOFs, including the drilling degree of
        freedom, not just 5 DOFs. Therefore it doesn't have the problem of
        undefined z-rotations.

    \item Deformations of the element are symmetric. A method of improving
    the corotational frame to keep the deformation symmetric is also
    presented in the paper.

    \item It is $C^1$ for the case of initial flat shape and, on the other cases, it is $C^0$ continuous on the edges and provides $C^1$ continuity in
    corners of the element. This is essential for good visual experience if
    high-resolution mesh is mapped on the mechanical mesh.

>>>>

@@

\FigureW{0.8\linewidth}{stages}
{Two stages of interpolation: First, from triangular with 6DOF nodes (a) a mesh of control points (b) is computed.
Then based on definition of the B\'ezier triangle a surface (c) is interpolated.}

@@

\Figure{0.6\linewidth}{bezier2}
{Cubic B\'ezier triangle with mesh of 10 control points.}

@@

The cubic B\'ezier triangles are defined by a mesh of 10 control points each, however the
simulated object is usually described by a triangular mesh possibly with normals.
A procedure for construction of initial B\'zier mesh is necessary.
We construct the initial B\'ezier mesh by taking into account the curvature of the triangular
mesh. Note that special care has to be taken to maintain
the continuity between elements across the nodes and edges, 
we partially employ the method described in \cite{Ubach2010} to maintain
$C^0$ continuity. Each of the control points on the edge is
computed as the intersection of:

@@

\Figure{0.6\linewidth}{segments2}
{Internal nodes of control mesh are connected to the corner nodes by kinematic link (shown in blue).}

@@

@@

Because the deflection field for the element is non-linear \eqref{eq-bez-delta}
in position the integrals \eqref{eq-Km} and \eqref{eq-Kb} have to be computed using
numerical integration. In our implementation we employ 6-point Gaussian
quadrature for integration over triangle area.
TODO: figure + gives the formula of the quadrature...
% TODO: add ref
% TODO: add abscissas/weights?

@@

Which means we use the same expression to interpolate the velocity only by
substituting the velocities at control points. 
For the corner control points  we
already have the velocities $V_i$. For the internal control points  we need to compute
them. We again make use of the kinematic link between control points and control points.
%solve the problem of computing the velocity of a point attached to the moving rigid body.
For the edge points we applied to motion of a rigid body:
%
\begin{eqnarray}
    V_j = V_i + \omega_i \times P_{i-j}
\end{eqnarray}
%
where $i$ is the index of the corner node the edge node is attached to and
$\omega_i$ is the angular velocity at the node. For the central node
the formula is based on the derivate of equation \eqref{eq-central2}:
%
\begin{eqnarray}
    V_{10} = \frac{1}{3} \sum_{i=1}^3 \left( V_i + \omega_i \times P_{i-10} \right)
\end{eqnarray}

@@

@@

\FigureW{\linewidth}{chd}
{Screenshots of the simulation system prototype for different surgical
procedures used to repair a coarctation of an aortic arch. The screenshots
are enriched with overlay delineations.}

Surgical interventions in infants with congenitally malformed great arteries
and hearts are extremely challenging due to the complex and heterogeneous
nature of their disease patterns. At present, cardiac surgeons rely on
non-invasive imaging for patient-specific examination and a set of preoperative
sketches with varying approaches to the surgical procedure. However, the most
promising approach is often chosen during the actual open-heart surgery, when
surgeons get a more concrete idea of possible outcomes.
The important decisions have to be made in very
short time and are strongly dependent on the surgeon's experience.

@@

@@

It fixes problems of the previous model \cite{Comas2010c} based on cubic
polynomials, namely: element is based on all 6 DOFs, deformations of the
element are symmetric, it is $C^1$ for the case of initial flat shape and, on
the other cases, it is $C^0$ continuous on the edges and provides $C^1$
continuity in corners of the element. This is essential for good visual
experience if high-resolution mesh is mapped on the mechanical mesh. A method
of improving the corotational frame to keep the deformation symmetric is also
presented in the paper.
